---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidycms

<!-- badges: start -->
<!-- badges: end -->

The goal of `tidycms` is to provide a set of functions to easily access public datasets from Centers for Medicare & Medicaid Services (CMS). The package is built on top of `httr2`. With user-friendly syntax, one can get a tidy tibble in a few lines of code.

Check the CMS API documentation at <https://data.cms.gov/api-docs/> and FAQs at <https://data.cms.gov/sites/default/files/2024-05/39b98adf-b5e0-4487-a19e-4dc5c1503d41/API%20Guide%20Formatted%201_5.pdf>.

## Installation

You can install the development version of tidycms from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JiaZhang42/tidycms")
```

## Example

This is a basic example which shows you how to glimpse all available datasets from CMS:

```{r example}
library(tidycms)
cms_datasets <- show_datasets()
cms_datasets
```

This table contains the basic information of all **latest** public datasets from CMS. Columns include 
- `title`
- `identifier`: the "Dataset Type Identifier", which doesn't change and always points to the latest version of the dataset. For "Dataset Version Identifier", visit its `landing_page`.
- `temporal`: time period
- `modified`: last modified date
- `description`
- `reference`: documentation link, named "describedBy" by CMS
- `landing_page`: webpage for the dataset

Alternatively, you can search for a specific dataset by keywords at [CMS website](https://data.cms.gov/search). 

Either way, you could get the identifier of the dataset you are interested in. For example, the identifier for the dataset "Accountable Care Organization Participants" is `9767cb68-8ea9-4f0b-8179-9431abc89f11`.

Then you can preview the first 10 rows of the dataset: 
```{r}
data_id <- '9767cb68-8ea9-4f0b-8179-9431abc89f11'
aco_participants <- slice_head_data(data_id, 10)
aco_participants
```

If you want to collect all data from a dataset, you can use the `collect_data()` function:
```{r}
data_id <- 'f1a8c197-b53d-4c24-9770-aea5d5a97dfb'
aco_participants_all <- collect_data(data_id, ask_for_confirmation = FALSE)
aco_participants_all
```
